NanoMaLy

### 2015-11-18 paper/pldi16-submission/evaluation-witness.tex

\section{Evaluation: Recasting Type Errors as Runtime Errors}
\label{sec:eval-witness}
%
The immediate question is ``What fraction of type errors admit
witnesses?''
%
To answer this question we implemented a prototype of our search
procedure for the pure subset of \ocaml, \ie \lang extended with
algebraic datatypes and records. 
%
In our implementation we instantiated \gensym with a simple random
generation of values, which we will show is more than sufficient for the
majority of type errors.
%
We evaluated our implementation of two sets of known-bad programs, \ie
programs that were rejected by the \ocaml compiler because of a type
error.
%
The first dataset comes from the Spring 2014 undergraduate Programming
Languages course at UC San Diego (IRB \#XXXXX). 
%
We recorded each interaction with the \ocaml top-level system over the
course of the first three assignments, from which we extracted XXXX
distinct, ill-typed \ocaml programs.
%
The second dataset -- widely used in the literature -- comes from a
similar course at the University of Washington~\cite{XXXXX}, from which
we extracted XXXX ill-typed programs.

>>>>

\section{Evaluation: Recasting Type Errors as Runtime Errors}
\label{sec:eval-witness}
%
The immediate question is ``What fraction of type errors admit
witnesses?''
%
To answer this question we implemented a prototype of our search
procedure for the pure subset of \ocaml, \ie \lang extended with
algebraic datatypes and records. 
%
In our implementation we instantiated \gensym with a simple random
generation of values, which we will show is more than sufficient for the
majority of type errors.
%
We evaluated our implementation of two sets of known-bad programs, \ie
programs that were rejected by the \ocaml compiler because of a type
error.
%
The first dataset comes from the Spring 2014 undergraduate Programming
Languages course at UC San Diego (IRB \#140608). 
%
We recorded each interaction with the \ocaml top-level system over the
course of the first three assignments, from which we extracted XXXX
distinct, ill-typed \ocaml programs.
%
The second dataset -- widely used in the literature -- comes from a
similar course at the University of
Washington~\cite{lerner_seminal:_2006}, from which we extracted 284
ill-typed programs.
